Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

\begin{lemma} \label{lmm:hv:type2:contained-h*}
    Both statements below are true: 
    \myenums{
        \item $\sum_{i=1}^k \sum_{r^* \in R^*_i} |\cross_H(r^*)| \le \out$.

>>>>

\begin{lemma} \label{lmm:hv:type2:contained-h*}
    Both statements below are true: 
    \myenums{
        \item $\sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)| \le \out$.

        \item Consider any tuple $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$. Set $h' = \bm{t}[k-2]$ and let $h^*$ be the minimal segment of $h'$. Then, we have $$\contained_{R_{k-2}}(\bm{t}) \subseteq \contained_{R_{k-2}}(h^*).$$ Furthermore, if the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ are sorted in descending order of $\xright(r)$, then $\contained_{R_{k-2}}(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}
